$N_{\text{eff}}$ priors

### 2015-05-24 Notes/N_eff_prior_paper.tex
new plots and Notes

% Group addresses by affiliation; use superscriptaddress for long
% author lists, or if there are many overlapping affiliations.
% For Phys. Rev. appearance, change preprint to twocolumn.
% Choose pra, prb, prc, prd, pre, prl, prstab, prstper, or rmp for journal
%  Add 'draft' option to mark overfull boxes with black boxes
%  Add 'showpacs' option to make PACS codes appear
%  Add 'showkeys' option to make keywords appear
\documentclass[aps,prl,preprint,groupedaddress]{revtex4-1}
%\documentclass[aps,prl,preprint,superscriptaddress]{revtex4-1}
%\documentclass[aps,prl,reprint,groupedaddress]{revtex4-1}
\usepackage{bm}
\usepackage{amsmath}
% You should use BibTeX and apsrev.bst for references
% Choosing a journal automatically selects the correct APS
% BibTeX style file (bst file), so only uncomment the line
% below if necessary.
%\bibliographystyle{apsrev4-1}

\begin{document}

@@

\begin{abstract}
Try to understand the effect of prior on the $N_{\text{eff}}$ parameter with a Fisher matrix approach. Where should you invest time and money if you really care about the value of $N_{\text{eff}}$?

@@

@@

\section{Data}
\section{Results}
\section{Conclusions}

>>>>

% Group addresses by affiliation; use superscriptaddress for long
% author lists, or if there are many overlapping affiliations.
% For Phys. Rev. appearance, change preprint to twocolumn.
% Choose pra, prb, prc, prd, pre, prl, prstab, prstper, or rmp for journal
%  Add 'draft' option to mark overfull boxes with black boxes
%  Add 'showpacs' option to make PACS codes appear
%  Add 'showkeys' option to make keywords appear
\documentclass[aps,prl,preprint,groupedaddress]{revtex4-1}
%\documentclass[aps,prl,preprint,superscriptaddress]{revtex4-1}
%\documentclass[aps,prl,reprint,groupedaddress]{revtex4-1}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{graphicx}

% You should use BibTeX and apsrev.bst for references
% Choosing a journal automatically selects the correct APS
% BibTeX style file (bst file), so only uncomment the line
% below if necessary.
%\bibliographystyle{apsrev4-1}

\begin{document}
\graphicspath{{../images/}}

@@

\begin{abstract}
Try to understand the effect of priors on different parameters on the $N_{\text{eff}}$ errors with a Fisher matrix approach. Where should you invest time and money if you really care about the value of $N_{\text{eff}}$?

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.6]{PS_phi_with_noise.pdf}
\caption{Lensing potential power spectrum for our fiducial cosmology together with the lensing reconstruction noise $N^{\phi}$ used in this work.}
\label{fig:phi-cl-noise}
\end{center}
\end{figure}

@@

\section{Data}
\section{Results}

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.6]{h0_fisher.pdf}
\caption{}
\label{fig:phi-cl-noise}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.6]{tau_fisher.pdf}
\caption{}
\label{fig:phi-cl-noise}
\end{center}
\end{figure}

\section{Conclusions}
